\documentclass[10pt,a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[left=1.0cm,right=1.0cm,top=1.0cm,bottom=1.0cm]{geometry}
\usepackage{fontspec}
\usepackage[english, bidi=basic, provide=*]{babel}

% Primary Font: Noto Sans - Clean, modern, and professional
\babelprovide[import, onchar=ids fonts]{english}
\babelfont{rm}{Noto Sans}
\babelfont{sf}{Noto Sans}

% --- PACKAGES ---
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{paracol}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fontawesome5} 
\usepackage{microtype} 

% --- COLORS ---
\definecolor{headerblue}{RGB}{20, 40, 80}      % Deep Navy
\definecolor{textgray}{RGB}{40, 40, 40}        % Dark Gray for better contrast
\definecolor{bulletcolor}{RGB}{50, 50, 50}

% --- FORMATTING ---
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{0.8cm}
\setstretch{1.12} 
\emergencystretch=1.5em 

% Section Header Stylings - Consistent with professional standards
\titleformat{\section}
  {\normalsize\bfseries\color{headerblue}}
  {}
  {0em}
  {\MakeUppercase}
  [\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Custom Job Entry Command
\newcommand{\job}[4]{
    \vspace{4pt} 
    \noindent
    {\small\bfseries\color{textgray} #1} \hfill {\footnotesize\bfseries #2} \\[1pt]
    {\scriptsize\textbf{\textit{\color{headerblue} #3}}} \hfill {\scriptsize\textit{#4}}
}

% Global List Settings
\setlist[itemize]{leftmargin=4mm, nosep, topsep=1pt, itemsep=1.5pt, label={\scriptsize\color{bulletcolor}\textbullet}}

% Hyperref setup
\hypersetup{colorlinks=false, hidelinks}

\begin{document}

% --- HEADER ---
\begin{center}
    {\huge\bfseries\color{headerblue} Venkata Murali Kumar Chintala} \\[3pt]
    {\normalsize\textbf{\color{textgray} Technical Lead \textbar\ Enterprise Solutions Architect}} \\[6pt]
    \footnotesize
    \faMapMarker* Visakhapatnam, India \quad \textbar \quad
    \faPhone* +91-9989225431 \quad \textbar \quad
    \faEnvelope \ muralikumar.ch@gmail.com \quad \textbar \quad
    \faLinkedin \ \href{https://linkedin.com/in/chvmuralikumar}{in/chvmuralikumar} \quad \textbar \quad
    \faGlobe \ \href{https://muralikumarch.github.io/java-portfolio/}{muralikumarch.io}
\end{center}

\vspace{2pt}

% --- LAYOUT START ---
\columnratio{0.72} 
\begin{paracol}{2}

\setlist[itemize]{leftmargin=3.5mm, itemsep=0.5pt, parsep=0pt, topsep=3pt}

% =====================
% LEFT COLUMN (EXPERIENCE)
% =====================
\section*{\faUser \hspace{4pt} Professional Profile}
\begin{spacing}{1.1} 
\scriptsize
Strategically focused \textbf{Technical Lead} with 15+ years of success performing at an \textbf{Architect level} to deliver digital transformation across \textbf{Azure and AWS} ecosystems. Expert in \textbf{Java Full Stack} development and AI Functional Architecture, specializing in designing scalable AI solutions, Agentic workflows, and enterprise-grade LLM orchestration. Proven track record in modernizing monolithic systems into resilient microservices while aligning complex business objectives with technical strategy, architectural excellence, and robust security models.
\end{spacing}

\section*{\faBriefcase \hspace{4pt} Professional Experience}

\scriptsize\job{Technical Lead / Solutions Architect}{July 2024 -- Present}{RCG Global Services (Myridius)}{Chennai, India}
\begin{itemize}
    \item \textbf{Designing and implementing} scalable AI solutions using \textbf{AWS AI Platform} and \textbf{Azure AI}, architecting functional designs that enhance system performance and align with strategic goals.
    \item \textbf{Developing AI functional architectures} to support complex business needs, integrating Agentic AI concepts and Generative AI technologies across multi-cloud platforms.
    \item \textbf{Leading the development} of Python-driven AI applications, orchestrating seamless integration between AI components and core \textbf{Java Full Stack} systems.
    \item \textbf{Providing technical guidance} on Prompt Engineering and architectural design patterns to ensure robust, reliable, and secure deployment of AI-driven functional workflows.
    \item \textbf{Overseeing cloud infrastructure} optimization for AI solutions, ensuring cost-efficiency and compliance with enterprise security models and industry best practices.
    \item \textbf{Collaborating with stakeholders} to translate business vision into high-level technical requirements and long-term architectural roadmaps.
\end{itemize}

\vspace{8pt} 
\job{Principal Java Developer}{Nov 2017 -- June 2024}{Parexel International}{Hyderabad, India}
\begin{itemize}
    \item \textbf{Spearheaded the technical transformation} of a global clinical data platform, migrating monolithic legacy systems to a modern \textbf{Angular / Spring Boot 3.x} microservices architecture.
    \item \textbf{Architected high-concurrency Java backends}, defining enterprise-wide standards for secure identity management, OAuth 2.0, and JWT for mission-critical healthcare data.
    \item \textbf{Engineered Event-Driven Architectures (EDA)} using Apache Kafka, facilitating real-time, fault-tolerant data synchronization across distributed enterprise modules.
    \item \textbf{Governed database strategy} and query optimization for large-scale Oracle and PostgreSQL environments, reducing contention and improving throughput by 35\%.
\end{itemize}

\vspace{8pt} 
\job{Senior Software Engineer}{Sep 2014 -- Nov 2017}{Parexel International}{Hyderabad, India}
\begin{itemize}
    \item \textbf{Architected distributed caching layers} using Redis, improving API response times by 30\% for high-traffic clinical portals.
    \item \textbf{Pioneered the adoption} of Docker containerization and automated CI/CD pipelines, standardizing delivery and reliability across the enterprise product suite.
    \item \textbf{Led technical architecture reviews} and governed code quality standards for large-scale enterprise deployments.
\end{itemize}

\vspace{8pt} 
\job{Senior Software Engineer}{Oct 2013 -- Sep 2014}{Kony IT Services}{Hyderabad, India}
\begin{itemize}
    \item \textbf{Directed the architectural strategy} for mobile middleware, ensuring seamless integration between Kony frontends and Java-based enterprise backends.
    \item \textbf{Implemented} secure mobile protocols and end-to-end encryption for mission-critical financial service applications.
\end{itemize}

\vspace{8pt} 
\job{Software Engineer}{Mar 2010 -- Oct 2013}{Wipro Technologies}{Hyderabad, India}
\begin{itemize}
    \item \textbf{Engineered} server-side business logic for high-transaction banking modules using Core Java and Spring, ensuring 99.9\% system stability.
    \item \textbf{Modernized} legacy PL/SQL procedures, optimizing complex data retrieval for global financial modules.
\end{itemize}

\switchcolumn
\setlist[itemize]{leftmargin=4mm, itemsep=2.5pt, parsep=0pt, topsep=1pt}

% =====================
% RIGHT COLUMN (SKILLS)
% =====================

\section*{\faCogs \hspace{4pt} Expertise}
\footnotesize
\textbf{Java Full Stack Mastery} \\
{\scriptsize Java 17+, Spring Boot 3.x, Angular, Hibernate, Spring Security, Kafka, Redis, PostgreSQL, Oracle}

\vspace{8pt}
\textbf{Functional AI Architecture} \\
{\scriptsize GenAI, Agentic AI, RAG Patterns, Prompt Engineering, AI Functional Design, Python Orchestration}

\vspace{8pt}
\textbf{Enterprise Architecture} \\
{\scriptsize Solution Design, Cloud Security Models, Multi-Cloud (Azure, AWS), EDA, Microservices, SaaS}

\vspace{8pt}
\textbf{Cloud Infrastructure} \\
{\scriptsize Azure AI Studio, AWS Bedrock, Kubernetes (AKS, EKS), Terraform, API Management}

\vspace{8pt}
\textbf{DevSecOps \& Quality} \\
{\scriptsize Azure DevOps, Jenkins, Docker, CI/CD, SonarQube, TDD, Agile/Jira}

\vspace{8pt}
\textbf{Productivity \& AI Tools} \\
{\scriptsize Microsoft Power Platform, GitHub Copilot, Claude Code, Cursor}

\vspace{12pt} 
\section*{\faAward \hspace{4pt} Certifications}
\scriptsize
\begin{itemize}[leftmargin=3mm, itemsep=3pt]
    \item \href{https://www.credly.com/badges/5e894b23-c4f7-4a0a-8c51-111e6cda5d9f}{AWS Certified AI Practitioner (2025)}
    \item \href{https://learn.microsoft.com/api/credentials/share/en-us/MuraliChintala/F5FCFCA4028552C1}{Azure AI Engineer Associate (2024)}
    \item \href{https://www.credly.com/badges/781d466b-8d24-470d-8564-f7a7f7747c74}{AWS Solutions Architect Assoc. (2026)}
    \item \href{https://www.credly.com/badges/7752e98a-4907-47c0-83c5-e24dad34ec82}{AWS Certified Developer Assoc. (2024)}
    \item \href{https://learn.microsoft.com/en-us/users/muralichintala/credentials/6c7fae34bf5fe202}{Azure Solutions Architect Expert (2022)}
    \item Azure Developer Associate (2021)
    \item Oracle Certified Programmer (2019)
\end{itemize}

\vspace{12pt} 
\section*{\faGraduationCap \hspace{4pt} Education}
\footnotesize
\textbf{Master of Computer Applications} \\
{\scriptsize Andhra University \textbar\ 2006}

\vspace{6pt}
\textbf{B.Sc. Computer Science} \\
{\scriptsize Andhra University \textbar\ 2003}

\end{paracol}

\end{document}
